Starcode: an exact algorithm for sequence clustering

### 2014-06-19 doc/document.tex
Added more information about the NW algorithm in caption of Fig 1.

\begin{figure}[!tpb]%figure1
\centerline{\includegraphics{Fig1.pdf}}
\caption{Needleman-Wunsch (NW) alignment. \textbf{a}
  Alignment of GTTGCA and GATCCA using
the NW alignment matrix. The margins (purple) are initialized and the cells of
the matrix (yellow) are computed from left to right and from top to bottom by a
dynamic programming algorithm. The Levenshtein distance distance between the two
sequences is found in the bottom right cell. \textbf{b}
Lower complexity algorithm to
determine whether GTTGCA and GATCCA are 2-neighbors. The values in purple cells
are set during initialization. The dynamic programming algorithm proceeds as above,
with the difference that it is interrupted if the value of a diagonal cell (bold
borders) is larger than 2. The values in purple cells are not always the same as
their equivalent in a (purple arrow), but the values in the yellow cells are
nevertheless identical. The values of the white cells are never computed, which
contributes to making the algorithm less complex.}\label{fig:01}
\end{figure}

>>>>

\begin{figure}[!tpb]%figure1
\centerline{\includegraphics{Fig1.pdf}}
\caption{Needleman-Wunsch (NW) alignment. \textbf{a}
  Alignment of GTTGCA and GATCCA using
the NW alignment matrix. The margins (purple) are initialized and the cells of
the matrix (yellow) are computed from left to right and from top to bottom by
the following
dynamic programming algorithm. The value in each cell is computed from the values
of the neighboring top, left and top-left cells. Denoting $a$, $b$ and $c$ these
respective terms, the value in the cell of coordinates $(i,j)$ is computed as
$\min(a+1, b+1, c)$ if the $i$-th letter from the first sequence is identical to
the $j$-th letter from the second, or $\min(a+1, b+1, c+1)$ if the letters are
different. The Levenshtein distance
between the two sequences is found in the bottom right cell. \textbf{b}
Lower complexity algorithm to
determine whether GTTGCA and GATCCA are 2-neighbors. The values in purple cells
are set during initialization. The dynamic programming algorithm proceeds as above,
with the difference that it is interrupted if the value of a diagonal cell (bold
borders) is larger than 2. The values in purple cells are not always the same as
their equivalent in a (purple arrow), but the values in the yellow cells are
nevertheless identical. The values of the white cells are never computed, which
contributes to making the algorithm less complex.}\label{fig:01}
\end{figure}
